### 2023-01-23 paper-thesis/chapters/30-comparing-with-haskell.tex
Compare with Haskell

>>>>

\section{Comparison}

The base implementations of the language are quite similar. One difference is the way the definitions are clustered\todo{not right word?}. In Statix, one could put each language construct in a separate file, keeping the definitions for that construct together. In the Haskell implementation this is not easily possible\footnote{We could still define a function that then calls the actual implementation in the separate files, but this is still inferior to the Statix implementation.}, since function definitions can not be split over a file.

Another advantage that Statix has is that it has first-order inference built-in, which makes implementing a basic form of inference as described in chapter \ref{ch:inference} way easier. However, if we want a more complex form of inference then an implementation in Haskell would be better, since it is a more expressive language and it has more libraries available.

Finally, creating the language in Spoofax automatically gives us editor services such as code highlighting and semantic autocompletion, as dicusssed in chapter \ref{chap:editor-services}. Implementing these in Haskell would require some work.
